\bf An observational study of papers published in \emph{PLOS ONE} and studies posted to a trial registry.

### 2021-04-22 manuscript/asa_template/asa_template.Rmd
update format of .xlsx boilerplate files

bibliography: references.bib
output: rticles::asa_article
fig_caption: yes
---

@@

```{r, echo=FALSE, fig.align='center', out.width="70%",fig.cap="\\label{fig:plos-n}PLOS summary"}

@@

API searches returned `r format(n.api,big.mark=',')` unique records, of which `r format(n.include,big.mark=',')` (`r perc.include`%) included a statistical methods section based on our search strategy. In the final sample, 95,518 (85%) DOIs returned an exact match against common section headings, including 64,133 for 'statistical analysis', 13,380 for 'statistical analyses' and 13,627 for 'data analysis'. Among DOIs that did not meet the partial matching criteria, initial search terms appeared in [TODO].

@@

The median length of statistical methods sections was `r n.words[['med']]` words (IQR: `r n.words[['q1']]` to `r n.words[['q3']]` words) (Figure \ref{fig:plos-n}B). `r format(n.extremes[['morethan500']],big.mark=',')` articles (`r p.extremes[['morethan500']]`%) had a statistical methods section of 500 words or more. `r format(n.extremes[['lessthan50']],big.mark=',')` articles (`r p.extremes[['lessthan50']]`%) had a statistical methods section of 50 words or less, equal to the length of this paragraph.

All papers included Biology and life sciences (n = `r format(n.biology,big.mark=',')`), Earth sciences
(n = `r format(n.earth,big.mark=',')`) and/or Computer and information sciences (n = `r format(n.computer,big.mark=',')`) in their top 3 subject classifications
(Figure \ref{fig:plos-n}C).

```{r, echo=FALSE, fig.align='center', out.width="70%", fig.cap="\\label{fig:plos-wordclouds}PLOS ONE topic clouds."}
knitr::include_graphics("figures/plos.wordclouds.jpg")
```

Increasing the number of clusters decreased cluster quality based on global goodness-of-fit measures (Supplementary Figure 1), with average silhouette score and within-cluster dispersion leveling off around 20 clusters. This indicated that the data comprised one large, heterogeneous cluster and multiple smaller clusters.

The topic clouds based on ten clusters are in Figure~\ref{fig:plos-wordclouds}. Frequently occurring words reflected the use of statistical software (Topics 3 and 5), descriptive statistics (Topic 6), group based hypothesis testing (Topics 1 and 4) and definitions of statistical significance (Topics~1 and 9). Statistical methods sections associated with regression (Topic 2) and meta-analysis (Topic 7) were also identified.

<!-- ```{r} -->
<!-- load('../../results/plos.results.10topics.rda') -->

<!-- ftab.plos = matches %>% -->
<!--   group_by(topic_id) %>% summarise(DOIs = n(),`Median word count` = median(words),Q1=quantile(words,.25),Q3=quantile(words,.75),.groups='drop')  -->

<!-- flextable(ftab.plos) -->

<!-- ``` -->

Topics related to the use of statistical software differentiated between Prism GraphPad (Topic~3: n = 9,879; 8.8%) and SPSS (Topic 5: n = 9,574; 8.6%) (Box 1). A manual review of the top matching sections in these topics showed strong evidence of boilerplate text. Nine out ten top matches for Topic 3 stated the use of Prism GraphPad but did not specify which statistical methods were used; six out of ten top matches returned the same cluster score indicating near identical text. Top matching sections for Topic 5 included information on SPSS version numbers and definitions of statistical significance.

* Results of cosine similaritites

```{r}
load('../../results/plos.cosinesim.10topics.rda')

ftab = flextable(ftab.cosine.plos) %>% theme_box() %>% autofit()
ftab <- set_caption(ftab, "Summary of cosine similarity scores among top 500 DOIs assigned to each topic: PLOS ONE")
ftab

@@

@@

```{r, echo=FALSE, fig.align='center', out.width="70%", fig.cap="ANZCTR topic clouds."}
knitr::include_graphics("figures/anzctr.wordclouds.jpg")
```

@@

>>>>

bibliography: references.bib
output: rticles::asa_article
header-includes:
      - \usepackage{pdflscape}
fig_caption: yes
---

@@

```{r, echo=FALSE, fig.align='center', out.width="60%",fig.cap="\\label{fig:plos-n}PLOS summary"}

@@

API searches returned `r format(n.api,big.mark=',')` results (DOIs), of which `r format(n.include,big.mark=',')` (`r perc.include`%) included a statistical methods section based on our search strategy. In the final sample, 95,518 (85%) DOIs returned an exact match against common section headings: 64,133 for 'statistical analysis', 13,380 for 'statistical analyses' and 13,627 for 'data analysis'.

Among DOIs that did not meet the partial matching criteria, initial search terms appeared in [TODO].

@@

Statistical methods sections had a median length of `r n.words[['med']]` words and inter-quartile range of `r n.words[['q1']]` to `r n.words[['q3']]` words (Figure \ref{fig:plos-n}B). `r format(n.extremes[['morethan500']],big.mark=',')` articles (`r p.extremes[['morethan500']]`%) had a statistical methods section of 500 words or more. `r format(n.extremes[['lessthan50']],big.mark=',')` articles (`r p.extremes[['lessthan50']]`%) had sections with 50 words or less, equal to the length of this paragraph.

All DOIs included Biology and life sciences (n = `r format(n.biology,big.mark=',')`), Earth sciences
(n = `r format(n.earth,big.mark=',')`) and/or Computer and information sciences (n = `r format(n.computer,big.mark=',')`) in their top 3 subject classifications
(Figure \ref{fig:plos-n}C).

<!-- Increasing the number of clusters decreased cluster quality based on global goodness-of-fit measures (Supplementary Figure 1), with average silhouette score and within-cluster dispersion leveling off around 20 clusters. This indicated that the data comprised one large, heterogeneous cluster and multiple smaller clusters. -->

```{r, echo=FALSE,fig.align='center', out.width="70%",fig.cap="\\label{fig:plos-clouds}Topic clouds for ten clusters for PLOS ONE"}

knitr::include_graphics("figures/plos.wordclouds.jpg")

@@

The topic clouds based on ten clusters are in Figure~\ref{fig:plos-clouds}. Frequently occurring words reflected the use of statistical software (Topics 3 and 5), descriptive statistics (Topic 6), group based hypothesis testing (Topics 1 and 4) and definitions of statistical significance (Topics~1 and 9). Statistical methods sections associated with regression (Topic 2) and meta-analysis (Topic 7) were also identified.

```{r}
load('../../results/plos.results.10topics.rda')

ftab.plos = matches %>%
  group_by(topic_id) %>% summarise(DOIs = n(),`Median word count` = median(words),Q1=quantile(words,.25),Q3=quantile(words,.75),.groups='drop')

flextable(ftab.plos)

Topics related to the use of statistical software differentiated between Prism GraphPad (Topic~3: n = 9,879; 8.8%) and SPSS (Topic 5: n = 9,574; 8.6%) . Manual review of results showed that nine out of the ten top matching DOIs for Topic 3 stated the use of Prism GraphPad, but did not specify which statistical methods were used. Top matching sections for Topic 5 included information on SPSS version numbers and definitions of statistical significance. Examples of boilerplate text for selected topics are presented in Table \ref{tab:plos-example-boilerplate}. Examples correspond to top ranking DOIs, and DOIs with the higher number of matches based on cosine similarity score greater than 0.8. Further results from cosine similarity scores are provided in Supplementary File 2.

```{r}
FitFlextableToPage <- function(ft, pgwidth = 8){

  ft_out <- ft %>% autofit()

  ft_out <- width(ft_out, width = dim(ft_out)$widths*pgwidth /(flextable_dim(ft_out)$widths))
  return(ft_out)
}
boilerplate.plos =  read.table(header=TRUE, sep='&', text='
Theme & Topic & Examples
Statistical software & 3 & GraphPad Prism (Graphpad Software, San Diego, CA) was used for all analyses.
Statistical software &3 & All statistical analysis was performed using Graphpad Prism software.
Statistical software & 5 & SPSS software version 17.0 (SPSS, Chicago, IL, USA) was used for statistical analysis.
Statistical software & 5  & The results are presented as the mean ± SEM. Data were analyzed by one-way ANOVA and LSD tests using the SPSS 13.0 software (SPSS Inc., Chicago, IL, USA). The difference was considered statistically significant at P<0.05.
Between-group hypothesis testing, two groups & 1 & Student’s t-test was used for statistical analysis. A p value of <0.05 was considered statistically significant.,
Between-group hypothesis testing, two groups& 1 & Statistical analysis was performed using the Students t-test. P values of less than 0.05 were considered significant
Between-group hypothesis testing, two groups& 9 & Statistical significance was determined by Students t-tests. * P<0.05, ** P = <0.01, *** P<0.001.
Between-group hypothesis testing, two groups& 9 & Data are presented as the mean ± SD. Statistical analysis was performed using the Students unpaired t-test. Differences were considered statistically significant at *p<0.05, **p<0.01 and ***p<0.001
Between-group hypothesis testing, two or more groups & 4 & Significant differences were determined using analysis of variance (ANOVA) followed by Tukey post-hoc tests for multiple comparisons.
Between-group hypothesis testing, two or more groups& 4 & Data are expressed as the mean ± SEM. Statistical analysis was performed using one-way analysis of variance (ANOVA) test, followed by Dunnett’s multiple comparison post hoc test. P values less than 0.05 were considered significant.
Descriptive statistics & 6 & All results are expressed as means ± standard deviation (± SD).
Descriptive statistics & 6 & Data are expressed as mean ± Standard error of the mean (SEM). Statistical analysis of the data was performed by the Student’s t-test. A value of P<0.05 was considered statistically significant.
')
boilerplate.plos = boilerplate.plos %>% mutate(Topic=replace_na(Topic,''))
ftab = flextable(boilerplate.plos) %>% empty_blanks %>% 
  merge_v(j=c('Theme','Topic')) %>% 
  theme_booktabs %>%
FitFlextableToPage
ftab

Definitions of statistical significance featured strongly in Topic 1 (n = 3,775) and Topic 9 (n = 6,104) combined with hypothesis testing for comparing differences between two groups. Topic 1 reflected applications of Student's t-test assuming a 5% level of statistical significance. Topic 9 referenced similar methods combined with multiple thresholds for declaring statistical significance by asterisk: ``$^{*}p<0.05$, $^{**}p<0.01$ and $^{***}p<0.001$''., a practice that has been criticised [add wasserstein2019].

Group-based hypothesis testing was a recurring theme across topics, with text descriptions varying based on method(s) used. One-way analysis of variance also featured strongly in Topic 4 (n = 10,163), with text citing common methods for performing post-hoc multiple comparisons. Top matching sections across these topics did not include definitions of groups being compared.

Frequently occurring words in Topic 6 (n = 4,746) including 'Mean', 'SD' and 'SEM' reflected the use of descriptive statistics for summarising continuous variables. Sections associated with this topic appeared to be expanded versions of Topics 1 and 9, showing evidence of boilerplate text in the form of descriptive statistics followed by hypothesis testing using Student's t-test, Mann Whitney U or one-way analysis of variance.

<!-- Remaining topics reflected applications of meta-analysis (Topic 7: n = 5,165), regression modelling (Topic 2: n = 19,478) and larger sections that reported data processing and statistical methods within the same section (Topic 8: n = 38,183).  -->

@@

@@

```{r, echo=FALSE, fig.align='center', out.width="70%", fig.cap="ANZCTR topic clouds."}

knitr::include_graphics("figures/anzctr.wordclouds.jpg")

### 2021-04-22 manuscript/asa_template/asa_template.tex
update format of .xlsx boilerplate files

@@

{\centering \includegraphics[width=0.7\linewidth]{figures/plos.summary}

@@

API searches returned 131,847 unique records, of which 111,731 (85\%)
included a statistical methods section based on our search strategy. In
the final sample, 95,518 (85\%) DOIs returned an exact match against
common section headings, including 64,133 for `statistical analysis',
13,380 for `statistical analyses' and 13,627 for `data analysis'. Among
DOIs that did not meet the partial matching criteria, initial search
terms appeared in {[}TODO{]}.

@@

The median length of statistical methods sections was 127 words (IQR: 61
to 254 words) (Figure \ref{fig:plos-n}B). 7,450 articles (7\%) had a
statistical methods section of 500 words or more. 19,461 articles (17\%)
had a statistical methods section of 50 words or less, equal to the
length of this paragraph.

All papers included Biology and life sciences (n = 107,584), Earth
sciences (n = 7,605) and/or Computer and information sciences (n =
5,190) in their top 3 subject classifications (Figure
\ref{fig:plos-n}C).

@@

\caption{\label{fig:plos-wordclouds}PLOS ONE topic clouds.}\label{fig:unnamed-chunk-5}
\end{figure}

Increasing the number of clusters decreased cluster quality based on
global goodness-of-fit measures (Supplementary Figure 1), with average
silhouette score and within-cluster dispersion leveling off around 20
clusters. This indicated that the data comprised one large,
heterogeneous cluster and multiple smaller clusters.

The topic clouds based on ten clusters are in
Figure\textasciitilde{}\ref{fig:plos-wordclouds}. Frequently occurring
words reflected the use of statistical software (Topics 3 and 5),
descriptive statistics (Topic 6), group based hypothesis testing (Topics
1 and 4) and definitions of statistical significance
(Topics\textasciitilde1 and 9). Statistical methods sections associated
with regression (Topic 2) and meta-analysis (Topic 7) were also
identified.

Topics related to the use of statistical software differentiated between
Prism GraphPad (Topic\textasciitilde3: n = 9,879; 8.8\%) and SPSS (Topic
5: n = 9,574; 8.6\%) (Box 1). A manual review of the top matching
sections in these topics showed strong evidence of boilerplate text.
Nine out ten top matches for Topic 3 stated the use of Prism GraphPad
but did not specify which statistical methods were used; six out of ten
top matches returned the same cluster score indicating near identical
text. Top matching sections for Topic 5 included information on SPSS
version numbers and definitions of statistical significance.

\begin{itemize}
\tightlist
\item
  Results of cosine similaritites
\end{itemize}

\includegraphics[width=6.13in,height=3.49in,keepaspectratio]{asa_template_files/figure-latex/unnamed-chunk-6-1.png}

@@

\caption{ANZCTR topic clouds.}\label{fig:unnamed-chunk-7}
\end{figure}

@@

@@

\includegraphics[width=4.66in,height=1.55in,keepaspectratio]{asa_template_files/figure-latex/unnamed-chunk-9-1.png}

@@

\caption{PLOS ONE clustering metrics.}\label{fig:unnamed-chunk-10}
\end{figure}

@@

\caption{PLOS ONE topic values.}\label{fig:unnamed-chunk-11}
\end{figure}

@@

\caption{ANZCTR clustering metrics.}\label{fig:unnamed-chunk-12}
\end{figure}

@@

\caption{ANZCTR topic values.}\label{fig:unnamed-chunk-13}
\end{figure}

>>>>

\usepackage{pdflscape}

@@

{\centering \includegraphics[width=0.6\linewidth]{figures/plos.summary}

@@

API searches returned 131,847 results (DOIs), of which 111,731 (85\%)
included a statistical methods section based on our search strategy. In
the final sample, 95,518 (85\%) DOIs returned an exact match against
common section headings: 64,133 for `statistical analysis', 13,380 for
`statistical analyses' and 13,627 for `data analysis'.

Among DOIs that did not meet the partial matching criteria, initial
search terms appeared in {[}TODO{]}.

@@

Statistical methods sections had a median length of 127 words and
inter-quartile range of 61 to 254 words (Figure \ref{fig:plos-n}B).
7,450 articles (7\%) had a statistical methods section of 500 words or
more. 19,461 articles (17\%) had sections with 50 words or less, equal
to the length of this paragraph.

All DOIs included Biology and life sciences (n = 107,584), Earth
sciences (n = 7,605) and/or Computer and information sciences (n =
5,190) in their top 3 subject classifications (Figure
\ref{fig:plos-n}C).

@@

\caption{\label{fig:plos-clouds}Topic clouds for ten clusters for PLOS ONE (left) and ANZCTR (right)}\label{fig:unnamed-chunk-5}
\end{figure}

The topic clouds based on ten clusters are in
Figure\textasciitilde{}\ref{fig:plos-clouds}. Frequently occurring words
reflected the use of statistical software (Topics 3 and 5), descriptive
statistics (Topic 6), group based hypothesis testing (Topics 1 and 4)
and definitions of statistical significance (Topics\textasciitilde1 and
9). Statistical methods sections associated with regression (Topic 2)
and meta-analysis (Topic 7) were also identified.

\includegraphics[width=3.75in,height=2.75in,keepaspectratio]{asa_template_files/figure-latex/unnamed-chunk-6-1.png}

Topics related to the use of statistical software differentiated between
Prism GraphPad (Topic\textasciitilde3: n = 9,879; 8.8\%) and SPSS (Topic
5: n = 9,574; 8.6\%) . Manual review of results showed that nine out of
the ten top matching DOIs for Topic 3 stated the use of Prism GraphPad,
but did not specify which statistical methods were used. Top matching
sections for Topic 5 included information on SPSS version numbers and
definitions of statistical significance. Examples of boilerplate text
for selected topics are presented in Table
\ref{tab:plos-example-boilerplate}. Examples correspond to top ranking
DOIs, and DOIs with the higher number of matches based on cosine
similarity score greater than 0.8. Further results from cosine
similarity scores are provided in Supplementary File 2.

\includegraphics[width=8.00in,height=4.12in,keepaspectratio]{asa_template_files/figure-latex/unnamed-chunk-7-1.png}

Definitions of statistical significance featured strongly in Topic 1 (n
= 3,775) and Topic 9 (n = 6,104) combined with hypothesis testing for
comparing differences between two groups. Topic 1 reflected applications
of Student's t-test assuming a 5\% level of statistical significance.
Topic 9 referenced similar methods combined with multiple thresholds for
declaring statistical significance by asterisk: ``\(^{*}p<0.05\),
\(^{**}p<0.01\) and \(^{***}p<0.001\)''., a practice that has been
criticised {[}add wasserstein2019{]}.

Group-based hypothesis testing was a recurring theme across topics, with
text descriptions varying based on method(s) used. One-way analysis of
variance also featured strongly in Topic 4 (n = 10,163), with text
citing common methods for performing post-hoc multiple comparisons. Top
matching sections across these topics did not include definitions of
groups being compared.

Frequently occurring words in Topic 6 (n = 4,746) including `Mean', `SD'
and `SEM' reflected the use of descriptive statistics for summarising
continuous variables. Sections associated with this topic appeared to be
expanded versions of Topics 1 and 9, showing evidence of boilerplate
text in the form of descriptive statistics followed by hypothesis
testing using Student's t-test, Mann Whitney U or one-way analysis of
variance.

@@

@@

\caption{ANZCTR topic clouds.}\label{fig:unnamed-chunk-9}
\end{figure}

@@

\includegraphics[width=4.66in,height=1.55in,keepaspectratio]{asa_template_files/figure-latex/unnamed-chunk-10-1.png}

@@

\caption{PLOS ONE clustering metrics.}\label{fig:unnamed-chunk-11}
\end{figure}

@@

\caption{PLOS ONE topic values.}\label{fig:unnamed-chunk-12}
\end{figure}

@@

\caption{ANZCTR clustering metrics.}\label{fig:unnamed-chunk-13}
\end{figure}

@@

\caption{ANZCTR topic values.}\label{fig:unnamed-chunk-14}
\end{figure}
